### 2022-07-25 paper/akweury/document.tex
update nnnn

\section{GCNN model evaluation}
The GCNN model is the base model of the whole thesis. In this section, we first discuss the noise filter performance of the model and then evaluate the performance on normal inference.

\subsection{Noise Filter Result}

@@

		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light_input.png}};
		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};

		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light.png}};
		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {Semi-dense Light Map};

@@

		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
	\end{tikzpicture}
	\caption{Light Net for light inpainting based on GCNN architecture.}
	\label{fig:light-net-archi}
\end{figure}

>>>>

\section{GCNN model evaluation}
The GCNN model is the base model of the whole thesis. In this section, we first evaluate the inpainting performance of the model based on light map input. Then we use the same model for normal inference task.

\subsection{Light Inpainting}
The light inpainting task in this section in order to evaluate the noise inpainting performance of GCNN model. It takes semi-dense light map as input to predict the fully dense light map, as shown in Figure \ref{fig:light-net-archi}.

@@

		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
		{\includegraphics[width=.2\textwidth]{./Figures/gcnn-synthetic/intrinsic_image_light_input.png}};
		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};

		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
		{\includegraphics[width=.2\textwidth]{./Figures/gcnn-synthetic/intrinsic_image_light.png}};
		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {fully-dense Light Map};

@@

		\node[text width=3.5cm] at (\vdist*\disttimes+0.3,\yschift-1) {GCNN};
	\end{tikzpicture}
	\caption{Light map inpainting based on GCNN architecture.}
	\label{fig:light-net-archi}
\end{figure}

The network is trained on 3000 light maps in the "synthetic-50-5" dataset with initial learning rate 0.001, learning schedule 8,1000 with decay factor 0.5, the batch size is 8, the feature map channel is 128 in all of the gated convolution layers. The result is shown in Table \ref{tab:light-inpainting}

	\centering
	\begin{tabular}{l l l l l l l l }
		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.} & over-perform\\
		LightNet  & 0.17  & 4.72 & &  & & & \\ 
		\hline
		GCNN  & 10.57 & 5.25 & 8 & 200,1600 & 0.5 & 0 & - \\
		\hline
		an3 & 10.46 & 64.86 & 8 & 3,12,1000  & 0.5 & 1 & yes\\
		\hline
		an3 & 10.81 & 65.34 & 8 & 10,1000  & 0.5 & 1 & no(yes) \\
		\hline
		VIL-1 & 10.50 & 31.57 & 8 & 10,1000 & 0.5 & 1 & yes \\
		\hline
		VIL-1 & 10.82 & 32.61 & 8 & 3,12,1000 & 0.5 & 1 & no(yes) \\
		\hline
		VIL-3  & 10.79 & 54.76 & 8 & 100,1000 & 0.1 & 3 & no(yes) \\
		\hline
		VIL-10  & 11.10 & 132.32 & 8 & 100,1000 & 0.1 &10 & no(yes)\\
	\end{tabular}
	\caption{The error of models. The angle error is the average angle error of all valid pixels in the test case. The time unit is millisecond. bz is the batch size, lr-schedule is learning rate schedule. lr-df is learning rate decay factor, l/i. Nr is the number of light-image maps used for each scene}	
	\label{tab:light-inpainting}
\end{table}
